Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-27 paper/paper-nature-revised.qmd
minor editorial revisions

---
title: "Digitization of the Australian Parliamentary Debates, 1998-2022"
number-sections: true
format: 
  pdf:
    keep-tex: true
bibliography: references.bib
csl: nature.csl
editor: visual
date: "now"
date-format: long
author:
  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
abstract: "Public knowledge of what is said in parliament is a tenet of democracy, and a critical resource for political science research. In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard. While the Australian Hansard has always been publicly available, it has been difficult to use for the purpose of large-scale macro- and micro-level text analysis because it has only been available as PDFs or XMLs. Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality, rectangular database that captures proceedings of the Australian parliamentary debates from 1998 to 2022. The database is publicly available and can be linked to other datasets such as election results. The creation and accessibility of this database enables the exploration of new questions and serves as a valuable resource for both researchers and policymakers."
---

@@

The official written record of parliamentary debates, **formally known as Hansard [@citehansard],** plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in many other Commonwealth countries, such as Canada and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad]. Having a digitized version of Hansard enables researchers to conduct text analysis and statistical modelling. Following the lead of that project, in this paper we introduce a similar database for Australia. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to **September** 2022, containing details on everything said in parliament in a form that can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.

**There are a wide variety of potential applications of this database. For instance, within Australia there is considerable concern that there has been a decline in the 'quality' of public policy debate (however that might be defined). Our dataset could be used to look at whether it is really getting worse in particular ways, and if so, why. We might also be interested in whether particular sub-populations are appropriately represented in what is talked about in parliament. For instance, there is often concern that regional areas are overlooked compared with metropolitan areas. Again, our database could be used to examine whether this has changed over time. We have developed our database in such a way that it could be linked with similar databases from other countries which would enable comparative analysis. For instance, we may be interested in how the policy focus of a parliament changes given various global events such as pandemics or wars. An international linkage provides a comparison case where domestic issues are different while international ones are common. As an example of enabling this linkage we have included PartyFacts IDs in our database. This should make it possible to link our database with other large parliamentary speech collection projects, such as ParlaMint [@Erjavec2022], ParlSpeech [@Rauh], ParlEE [@parlee], and MAPLE [@maple].**

@@

At present, the Hansard format that is available on the Parliament of Australia website is not easily accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created [@sherratt]. These data can be navigated by year, parliament, people, and bills [@sherratt]. To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created @Leslie_2021_HoR_Aus. Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol. **And finally, there has been examination of speech and MP level data between 1990 and 2019 in Australia @Dowding2021. Like us they scrape the Hansard record and link it with biographical data. The key difference is that our focus is on the database itself, while they are focused on using a database constructed from the same source to answer a particular question about speaker time. This different focus leads to different emphasis and approaches.**

@@

This section is structured as follows. First, we provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed the scripts used to create our database. This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure. Next we will explain the specific differences between the scripts, and outline what structural changes necessitated their separate development. We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions. Further, we discuss the script we developed to fill in remaining missing details on the MP speaking, which each file in our database was passed to after being parsed and cleaned. **Finally, we review the supplementary Hansard debate topics dataset and supplementary divisions dataset we created to expand the versatility of our database.**

@@

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child nodes, where the first child node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child node which has a `<subdebate.2>` child node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the MP whose turn it is to speak and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@@

![Snapshot of the beginning of the XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}

@@

The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014. These contain all parsed text elements, where each statement is separated onto its own row with details about the MP who is speaking, and rows are maintained in chronological order. This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<subdebate.1>` versus `<subdebate.2>`. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by the Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days. Details on these are provided in @sec-interject.

@@

Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files. The earliest sitting day this first script can successfully parse is 14 August 2012. Before developing new scripts to parse earlier Hansard documents, we prioritized cleaning and finalizing what we had been able to parse. As such we continued building our script, fixing any problems we noticed in the resulting datasets such as excess whitespace or spacing issues, and splitting up any additional sections of the parsed text onto separate rows where necessary. Specifically, we added a section of our script to separate out general stage directions. More information on this separation will be provided in @sec-stage. After completing our first script, it was formatted as a function which takes a single file name argument and produces one CSV file containing data on all proceedings from the given sitting day.

@@

As mentioned, we developed a total of four scripts to parse the 1998-2022 time frame of Hansard documents. Two main factors motivated us to create four scripts as opposed to just one, the first being structural variation in XML over time, and the second being improved computational efficiency with separate scripts. While all four scripts use the same general approach to parsing described in @sec-overview and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.

@@

![Portion of XML file for Hansard on 12 December 2002](patternEX.png){#fig-patternEX width="315"}

@@

We then added binary flags to differentiate between questions and answers. To do this in the first and second scripts, we separately re-parsed question and answer content using the XPath expressions `"chamber.xscript//question"` and `"chamber.xscript//answer"`, added the correct question and answer flags accordingly, and then added those flags back to the main dataframe based on exact text matches. For the third and fourth scripts, we made use of the fact that the patterns preceding text transcribed under a question node were stored separately from those transcribed under an answer node. As a result, we could readily use those patterns to flag questions and answers correctly based on which list of patterns it belonged to. Sometimes, **we identified** questions **which** were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags. For instance, we check for any statements flagged as questions which include the phrase "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer. **It is important to note, however, that because we identified and corrected for these transcription errors manually as we discovered them, additional flagging errors may exist which we did not catch. As such, users may identify and should be wary of occasional incorrectly flagged questions or answers in the data.**

@@

As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child nodes which exist to capture the structure of interruptions in that speech. @fig-xml3 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech. Looking at the element names highlighted in blue, these child nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`. We decided not to include this data in our final database, as it is embedded in our resulting datasets which have a flag for interjections.

![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}

We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day. We added the names of all MPs in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard. When an MP interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name. There is also variation in the capitalization of these names.[^1] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written. Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case. This variation demands careful consideration when writing regular expression patterns. In these lists we also accounted for any general interjection statements that were not attributed to an individual, such as "An opposition member interjecting-".

[^1]: Sometimes when someone's first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.

@@

![First 10 rows of the lookup table from 19 October 2017 Hansard processing](lookup_ex.png){#fig-lookup width="448"}

@@

![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}

Having developed a successful methodology for splitting interjections, we used this to inform our general approach in the third and fourth scripts. However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology. As discussed in @sec-diff, we used string patterns extracted from `<talk.start>` nodes to separate speeches. As evident in @fig-xml3, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process. In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process. This meant that we did not need to create lists of names and titles for which to search in the text as we did before. However, we used the same list of general interjection statements on which to separate as was used in the first two scripts. We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed.[^2]

[^2]: While most statements were categorized in their own child node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

@@

![10 rows of the pattern lookup table from 12 December 2012 Hansard processing](pattern_lookup.png){#fig-patterns}

@@

When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by MPs. Stage directions are general statements included in the transcript to document happenings in parliament. Examples of stage directions are "Bill read a second time", "Question agreed to", or "Debate adjourned". It was unclear to us from the XML and PDF who exactly these statements were attributed to. For further clarification, we watched portions of the video recording for some sitting days, and noticed that while these statements are documented in Hansard, they are not explicitly stated in parliament. For example, when the Deputy Speaker says "The question is that the bill be now read a second time", MPs vote, and if the majority is in favour, they proceed reading the bill the second time. This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to. Bill read a second time". For this reason, we filled the name variable for these statements with "stage direction". Stage directions were not flagged as interjections. These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches. We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts. **Despite our best efforts to capture all stage directions in this list, because it had to be built manually, users should be aware that it is possible that some stage directions were not separated onto their own rows in the process. Further, it is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do. However, they provide valuable information about the inner-workings and structure of parliamentary events. If the focus of the user’s research does not require stage directions, then this can be removed by filtering observations in `name` equal to “business start”, or “stage direction”.**

@@

**To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing debate topics and their corresponding page numbers for each sitting day in our database. To extract these data, we wrote a script to parse debate and sub-debate 1 information elements from each XML file in chronological order using the XPath expression "`//debate/debateinfo | //subdebate.1/subdebateinfo`", and added a date variable with the date of each sitting day. Note that in some cases there were multiple page number child nodes for the same debate or sub-debate title, likely due to manual transcription error. Upon manual inspection, we found that most often, the second page number node contained the same page number as the first node, and sometimes the second node contained a repeated debate title or a timestamp. Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset. After summarizing, these topics can be added to the main text by joining, and example code is provided in the README.**

@@

**Another fundamental component of parliamentary proceedings is voting. In the House, when a question arises such as "The question is that the amendment be agreed to", Members are asked to cast their vote either in the affirmative or in the negative, and the majority of votes as judged by the Speaker determines the outcome [@australia2018house]. Further, Members can vote in an unofficial arrangement called pairs, which "can be used to enable a Member on one side of the House to be absent for any votes when a Member from the other side is to be absent at the same time or when, by agreement, a Member abstains from voting" @australia2018house. If the result as determined by the Speaker is challenged by more than one MP, this leads to a division of the House in which the question is re-stated and Members must move to the left or right of their chair depending on how they vote, so that the votes can be re-counted and recorded [@australia2018house].**

**In the Hansard XML files, divisions data are structured outside of the `<speech>` content in their own `<division>` nodes that contain the voting data and division result. Since we focus primarily on the spoken `<speech>` Hansard content, our parsing scripts do not necessarily capture all divisions data from House proceedings. Our approach to parsing Hansard in the third and fourth scripts described in @sec-diff naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not. To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame. To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any timestamps where available, and did any additional data cleaning as necessary. We used a series of if-else statements in this script to account for variation in the structure of the `<division>` node over time. Finally, we then added a date variable to distinguish between sitting days.**

@@

Our database is available in both CSV and parquet formats. **Both CSV and parquet are open standards. We provide both because while CSVs are commonly used and can be manually inspected, parquet files are typically smaller and preserve class.** Our database covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 **where an XML transcript is available**, so there are **1,532 individual sitting day** files for each format. **Additionally, there is a single corpus file in both CSV and parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days. There is also a CSV and parquet file containing all parsed debate topics.** All data records are available on the general-purpose repository Zenodo, at <https://doi.org/10.5281/zenodo.7336075> [@katz_2023]. For each **Hansard data** file, **that is, the corpus and the individual sitting day files**, each row contains an individual statement, with details on the individual speaking. For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified. @tbl-vars provides an overview of each variable found in the **Hansard data files in the** database.

@@

**Finally, our database contains a file with all parsed divisions data in our timeframe. This is called `division_data`, and is available in RDA form and in parquet form. The reason it is not available in CSV form is because three of the variables (`names_AYES`, `names_NOES`, and `names_PAIRS`) are lists, which are not supported by the CSV rectangular data structure. The variables found in these data are summarized below, in @tbl-divisions.**

@@

We developed a script to perform automated tests on each file in our database, to enhance its quality and consistency. Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^4] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date. We validated that our file name and date was correct by checking the official PDF release from that sitting day.

[^4]: As seen in @fig-xml1, the first child node of the `<session.header>` element is the date.

The second test is designed to test for duplication errors in the data, by checking whether two lines that immediately follow each other have the same body (i.e. spoken content). This test detected **131** dates on which duplicate statements were made, and one immediately follows the other. Note that this test does not account for who is making each statement, meaning one MP repeating the words of another MP would be picked up in this test as well. We checked a sample of 40% of these duplicates, and manually validated that they are all repeated statements that do exist and are transcribed closely together in that day's XML file, and by our method should be parsed such that one of these statements is immediately followed by the other.

>>>>

---
title: "Digitization of the Australian Parliamentary Debates, 1998-2022"
number-sections: false
format: 
  pdf:
    keep-tex: true
bibliography: references.bib
csl: nature.csl
editor: visual
date: "now"
date-format: long
author:
  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
abstract: "Public knowledge of what is said in parliament is a tenet of democracy, and a critical resource for political science research. In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard. While the Australian Hansard has always been publicly available, it has been difficult to use for the purpose of large-scale macro- and micro-level text analysis because it has only been available as PDFs or XMLs. Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality, rectangular database that captures proceedings of the Australian parliamentary debates from 1998 to 2022. The database is publicly available and can be linked to other datasets such as election results. The creation and accessibility of this database enables the exploration of new questions and serves as a valuable resource for both researchers and policymakers."
---

@@

The official written record of parliamentary debates, formally known as Hansard [@citehansard], plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in many other Commonwealth countries, such as Canada and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad]. Having a digitized version of Hansard enables researchers to conduct text analysis and statistical modelling. Following the lead of that project, in this paper we introduce a similar database for Australia. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to September 2022, containing details on everything said in parliament in a form that can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.

There are a wide variety of potential applications of this database. For instance, within Australia there is considerable concern that there has been a decline in the 'quality' of public policy debate (however that might be defined). Our dataset could be used to look at whether it is really getting worse in particular ways, and if so, why. We might also be interested in whether particular sub-populations are appropriately represented in what is talked about in parliament. For instance, there is often concern that regional areas are overlooked compared with metropolitan areas. Again, our database could be used to examine whether this has changed over time. We have developed our database in such a way that it could be linked with similar databases from other countries which would enable comparative analysis. For instance, we may be interested in how the policy focus of a parliament changes given various global events such as pandemics or wars. An international linkage provides a comparison case where domestic issues are different while international ones are common. As an example of enabling this linkage we have included PartyFacts IDs in our database. This should make it possible to link our database with other large parliamentary speech collection projects, such as ParlaMint [@Erjavec2022], ParlSpeech [@Rauh], ParlEE [@parlee], and MAPLE [@maple].

@@

At present, the Hansard format that is available on the Parliament of Australia website is not easily accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created [@sherratt]. These data can be navigated by year, parliament, people, and bills [@sherratt]. To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created @Leslie_2021_HoR_Aus. Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol. And finally, there has been examination of speech and MP level data between 1990 and 2019 in Australia @Dowding2021. Like us they scrape the Hansard record and link it with biographical data. The key difference is that our focus is on the database itself, while they are focused on using a database constructed from the same source to answer a particular question about speaker time. This different focus leads to different emphasis and approaches.

@@

This section is structured as follows. First, we provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed the scripts used to create our database. This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure. Next we will explain the specific differences between the scripts, and outline what structural changes necessitated their separate development. We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions. Further, we discuss the script we developed to fill in remaining missing details on the MP speaking, which each file in our database was passed to after being parsed and cleaned. Finally, we review the supplementary Hansard debate topics dataset and supplementary divisions dataset we created to expand the versatility of our database.

@@

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child nodes, where the first child node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child node which has a `<subdebate.2>` child node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the MP whose turn it is to speak and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will [follow](#sec-qa).

@@

![Snapshot of the beginning of the XML file for Hansard on 25 February 2020](xml1.jpg){#fig-xml1}

@@

The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014. These contain all parsed text elements, where each statement is separated onto its own row with details about the MP who is speaking, and rows are maintained in chronological order. This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<subdebate.1>` versus `<subdebate.2>`. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by the Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days. Details on these are provided in the Interjections [section](#sec-interject) to follow.

@@

Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files. The earliest sitting day this first script can successfully parse is 14 August 2012. Before developing new scripts to parse earlier Hansard documents, we prioritized cleaning and finalizing what we had been able to parse. As such we continued building our script, fixing any problems we noticed in the resulting datasets such as excess whitespace or spacing issues, and splitting up any additional sections of the parsed text onto separate rows where necessary. Specifically, we added a section of our script to separate out general stage directions. More information on this separation will be provided in the subsequent Stage Directions [section](#sec-stage). After completing our first script, it was formatted as a function which takes a single file name argument and produces one CSV file containing data on all proceedings from the given sitting day.

@@

As mentioned, we developed a total of four scripts to parse the 1998-2022 time frame of Hansard documents. Two main factors motivated us to create four scripts as opposed to just one, the first being structural variation in XML over time, and the second being improved computational efficiency with separate scripts. While all four scripts use the same general approach to parsing described in the Overview [section](#sec-overview) and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.

@@

![Portion of XML file for Hansard on 12 December 2002](patternEX.jpg){#fig-patternEX width="315"}

@@

We then added binary flags to differentiate between questions and answers. To do this in the first and second scripts, we separately re-parsed question and answer content using the XPath expressions `"chamber.xscript//question"` and `"chamber.xscript//answer"`, added the correct question and answer flags accordingly, and then added those flags back to the main dataframe based on exact text matches. For the third and fourth scripts, we made use of the fact that the patterns preceding text transcribed under a question node were stored separately from those transcribed under an answer node. As a result, we could readily use those patterns to flag questions and answers correctly based on which list of patterns it belonged to. Sometimes, we identified questions which were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags. For instance, we check for any statements flagged as questions which include the phrase "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer. It is important to note, however, that because we identified and corrected for these transcription errors manually as we discovered them, additional flagging errors may exist which we did not catch. As such, users may identify and should be wary of occasional incorrectly flagged questions or answers in the data.

@@

As mentioned in the Script Differences [section](#sec-diff), more recent years of Hansard XMLs contain a series of child nodes which exist to capture the structure of interruptions in that speech. @fig-xml2 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech. Looking at the element names highlighted in blue, these child nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml2, we were able to extract useful details on the individual interjecting which we could use later. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`. We decided not to include this data in our final database, as it is embedded in our resulting datasets which have a flag for interjections.

![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml2.jpg){#fig-xml2 width="345"}

We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day. We added the names of all MPs in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard. When an MP interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name. There is also variation in the capitalization of these names. Sometimes when someone's first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized. Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written. Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case. This variation demands careful consideration when writing regular expression patterns. In these lists we also accounted for any general interjection statements that were not attributed to an individual, such as "An opposition member interjecting-".

@@

![First 10 rows of the lookup table from 19 October 2017 Hansard processing](lookup_ex.jpg){#fig-lookup width="448"}

@@

![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.jpg){#fig-interject}

Having developed a successful methodology for splitting interjections, we used this to inform our general approach in the third and fourth scripts. However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology. As discussed in the Script Differences [section](#sec-diff), we used string patterns extracted from `<talk.start>` nodes to separate speeches. As evident in @fig-xml2, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process. In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process. This meant that we did not need to create lists of names and titles for which to search in the text as we did before. However, we used the same list of general interjection statements on which to separate as was used in the first two scripts. We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed. In particular, while most statements were categorized in their own child node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

@@

![10 rows of the pattern lookup table from 12 December 2012 Hansard processing](pattern_lookup.jpg){#fig-patterns}

@@

When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by MPs. Stage directions are general statements included in the transcript to document happenings in parliament. Examples of stage directions are "Bill read a second time", "Question agreed to", or "Debate adjourned". It was unclear to us from the XML and PDF who exactly these statements were attributed to. For further clarification, we watched portions of the video recording for some sitting days, and noticed that while these statements are documented in Hansard, they are not explicitly stated in parliament. For example, when the Deputy Speaker says "The question is that the bill be now read a second time", MPs vote, and if the majority is in favour, they proceed reading the bill the second time. This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to. Bill read a second time". For this reason, we filled the name variable for these statements with "stage direction". Stage directions were not flagged as interjections. These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches. We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts. Despite our best efforts to capture all stage directions in this list, because it had to be built manually, users should be aware that it is possible that some stage directions were not separated onto their own rows in the process. Further, it is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do. However, they provide valuable information about the inner-workings and structure of parliamentary events. If the focus of the user's research does not require stage directions, then this can be removed by filtering observations in `name` equal to "business start", or "stage direction".

@@

To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing debate topics and their corresponding page numbers for each sitting day in our database. To extract these data, we wrote a script to parse debate and sub-debate 1 information elements from each XML file in chronological order using the XPath expression "`//debate/debateinfo | //subdebate.1/subdebateinfo`", and added a date variable with the date of each sitting day. Note that in some cases there were multiple page number child nodes for the same debate or sub-debate title, likely due to manual transcription error. Upon manual inspection, we found that most often, the second page number node contained the same page number as the first node, and sometimes the second node contained a repeated debate title or a timestamp. Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset. After summarizing, these topics can be added to the main text by joining, and example code is provided in the README.

@@

Another fundamental component of parliamentary proceedings is voting. In the House, when a question arises such as "The question is that the amendment be agreed to", Members are asked to cast their vote either in the affirmative or in the negative, and the majority of votes as judged by the Speaker determines the outcome [@australia2018house]. Further, Members can vote in an unofficial arrangement called pairs, which "can be used to enable a Member on one side of the House to be absent for any votes when a Member from the other side is to be absent at the same time or when, by agreement, a Member abstains from voting" @australia2018house. If the result as determined by the Speaker is challenged by more than one MP, this leads to a division of the House in which the question is re-stated and Members must move to the left or right of their chair depending on how they vote, so that the votes can be re-counted and recorded [@australia2018house].

In the Hansard XML files, divisions data are structured outside of the `<speech>` content in their own `<division>` nodes that contain the voting data and division result. Since we focus primarily on the spoken `<speech>` Hansard content, our parsing scripts do not necessarily capture all divisions data from House proceedings. Our approach to parsing Hansard in the third and fourth scripts described in the Script Differences [section](#sec-diff) naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not. To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame. To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any timestamps where available, and did any additional data cleaning as necessary. We used a series of if-else statements in this script to account for variation in the structure of the `<division>` node over time. Finally, we then added a date variable to distinguish between sitting days.

@@

Our database is available in both CSV and parquet formats. Both CSV and parquet are open standards. We provide both because while CSVs are commonly used and can be manually inspected, parquet files are typically smaller and preserve class. Our database covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 where an XML transcript is available, so there are 1,532 individual sitting day files for each format. Additionally, there is a single corpus file in both CSV and parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days. There is also a CSV and parquet file containing all parsed debate topics. All data records are available on the general-purpose repository Zenodo, at <https://doi.org/10.5281/zenodo.7336075> [@katz_2023]. For each Hansard data file, that is, the corpus and the individual sitting day files, each row contains an individual statement, with details on the individual speaking. For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified. @tbl-vars provides an overview of each variable found in the Hansard data files in the database.

@@

Finally, our database contains a file with all parsed divisions data in our timeframe. This is called `division_data`, and is available in RDA form and in parquet form. The reason it is not available in CSV form is because three of the variables (`names_AYES`, `names_NOES`, and `names_PAIRS`) are lists, which are not supported by the CSV rectangular data structure. The variables found in these data are summarized below, in @tbl-divisions.

@@

We developed a script to perform automated tests on each file in our database, to enhance its quality and consistency. Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header. This XML component can be seen in @fig-xml1, where the first child node of the `<session.header>` element is the date. Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date. We validated that our file name and date was correct by checking the official PDF release from that sitting day.

The second test is designed to test for duplication errors in the data, by checking whether two lines that immediately follow each other have the same body (i.e. spoken content). This test detected 131 dates on which duplicate statements were made, and one immediately follows the other. Note that this test does not account for who is making each statement, meaning one MP repeating the words of another MP would be picked up in this test as well. We checked a sample of 40% of these duplicates, and manually validated that they are all repeated statements that do exist and are transcribed closely together in that day's XML file, and by our method should be parsed such that one of these statements is immediately followed by the other.
